---
title: "Project - Report"
author: "George Surilas"
date: "April 7, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)
library(tokenizers)
library(gutenbergr)
library(rvest)
library(ggrepel)
library(reshape2)
```


```{r Wiki Bios Sentiment Analysis, echo = FALSE, cache = TRUE, message = FALSE}
urls <- c("https://en.wikipedia.org/wiki/Fyodor_Dostoevsky",
          "https://en.wikipedia.org/wiki/Leo_Tolstoy",
          "https://en.wikipedia.org/wiki/Nikolai_Gogol",
          "https://en.wikipedia.org/wiki/Ivan_Turgenev",
          "https://en.wikipedia.org/wiki/Anton_Chekhov",
          "https://en.wikipedia.org/wiki/Maxim_Gorky",
          "https://en.wikipedia.org/wiki/Yevgeny_Zamyatin",
          "https://en.wikipedia.org/wiki/Alexander_Pushkin",
          "https://en.wikipedia.org/wiki/Aleksandr_Solzhenitsyn",
          "https://en.wikipedia.org/wiki/Vladimir_Nabokov",
          "https://en.wikipedia.org/wiki/Mikhail_Bulgakov",
          "https://en.wikipedia.org/wiki/Ivan_Bunin",
          "https://en.wikipedia.org/wiki/Ivan_Goncharov",
          "https://en.wikipedia.org/wiki/Varlam_Shalamov",
          "https://en.wikipedia.org/wiki/Boris_Pasternak",
          "https://en.wikipedia.org/wiki/Mikhail_Lermontov",
          "https://en.wikipedia.org/wiki/Mikhail_Sholokhov",
          "https://en.wikipedia.org/wiki/Vasily_Grossman",
          "https://en.wikipedia.org/wiki/Lyudmila_Ulitskaya",
          "https://en.wikipedia.org/wiki/Marina_Tsvetaeva",
          "https://en.wikipedia.org/wiki/Evgeny_Chirikov",
          "https://en.wikipedia.org/wiki/Sergei_Yesenin",
          "https://en.wikipedia.org/wiki/Anna_Akhmatova",
          "https://en.wikipedia.org/wiki/Sophia_Parnok",
          "https://en.wikipedia.org/wiki/Maria_Rybakova",
          "https://en.wikipedia.org/wiki/Ernest_Hemingway",
          "https://en.wikipedia.org/wiki/William_Faulkner",
          "https://en.wikipedia.org/wiki/Toni_Morrison",
          "https://en.wikipedia.org/wiki/Maya_Angelou",
          "https://en.wikipedia.org/wiki/F._Scott_Fitzgerald",
          "https://en.wikipedia.org/wiki/Mark_Twain",
          "https://en.wikipedia.org/wiki/John_Steinbeck",
          "https://en.wikipedia.org/wiki/Nathaniel_Hawthorne",
          "https://en.wikipedia.org/wiki/Ralph_Ellison",
          "https://en.wikipedia.org/wiki/Herman_Melville",
          "https://en.wikipedia.org/wiki/Philip_Roth",
          "https://en.wikipedia.org/wiki/Edith_Wharton",
          "https://en.wikipedia.org/wiki/Harper_Lee",
          "https://en.wikipedia.org/wiki/Joseph_Heller",
          "https://en.wikipedia.org/wiki/Kurt_Vonnegut",
          "https://en.wikipedia.org/wiki/Emily_Dickinson",
          "https://en.wikipedia.org/wiki/J._D._Salinger",
          "https://en.wikipedia.org/wiki/James_Baldwin",
          "https://en.wikipedia.org/wiki/Sylvia_Plath",
          "https://en.wikipedia.org/wiki/Thomas_Pynchon",
          "https://en.wikipedia.org/wiki/Ray_Bradbury",
          "https://en.wikipedia.org/wiki/Truman_Capote",
          "https://en.wikipedia.org/wiki/Sinclair_Lewis",
          "https://en.wikipedia.org/wiki/Tennessee_Williams",
          "https://en.wikipedia.org/wiki/Sherwood_Anderson",
          "https://en.wikipedia.org/wiki/Raymond_Chandler",
          "https://en.wikipedia.org/wiki/Henry_David_Thoreau",
          "https://en.wikipedia.org/wiki/Flannery_O%27Connor",
          "https://en.wikipedia.org/wiki/Albert_Camus",
          "https://en.wikipedia.org/wiki/Marcel_Proust",
          "https://en.wikipedia.org/wiki/Gustave_Flaubert",
          "https://en.wikipedia.org/wiki/Victor_Hugo",
          "https://en.wikipedia.org/wiki/%C3%89mile_Zola",
          "https://en.wikipedia.org/wiki/Honor%C3%A9_de_Balzac",
          "https://en.wikipedia.org/wiki/Voltaire",
          "https://en.wikipedia.org/wiki/Jean-Paul_Sartre",
          "https://en.wikipedia.org/wiki/Moli%C3%A8re",
          "https://en.wikipedia.org/wiki/Simone_de_Beauvoir",
          "https://en.wikipedia.org/wiki/Alexandre_Dumas",
          "https://en.wikipedia.org/wiki/Charles_Baudelaire",
          "https://en.wikipedia.org/wiki/Jules_Verne",
          "https://en.wikipedia.org/wiki/Guy_de_Maupassant",
          "https://en.wikipedia.org/wiki/Arthur_Rimbaud",
          "https://en.wikipedia.org/wiki/Fran%C3%A7ois_Rabelais",
          "https://en.wikipedia.org/wiki/Denis_Diderot",
          "https://en.wikipedia.org/wiki/Ren%C3%A9_Descartes",
          "https://en.wikipedia.org/wiki/Georges_Perec",
          "https://en.wikipedia.org/wiki/Marquis_de_Sade",
          "https://en.wikipedia.org/wiki/Stendhal",
          "https://en.wikipedia.org/wiki/Charles_Dickens",
          "https://en.wikipedia.org/wiki/Jane_Austen",
          "https://en.wikipedia.org/wiki/Charlotte_Bront%C3%AB",
          "https://en.wikipedia.org/wiki/George_Eliot",
          "https://en.wikipedia.org/wiki/J._R._R._Tolkien",
          "https://en.wikipedia.org/wiki/J._K._Rowling",
          "https://en.wikipedia.org/wiki/George_Orwell",
          "https://en.wikipedia.org/wiki/Thomas_Hardy",
          "https://en.wikipedia.org/wiki/William_Shakespeare",
          "https://en.wikipedia.org/wiki/Virginia_Woolf",
          "https://en.wikipedia.org/wiki/Joseph_Conrad",
          "https://en.wikipedia.org/wiki/C._S._Lewis",
          "https://en.wikipedia.org/wiki/Roald_Dahl",
          "https://en.wikipedia.org/wiki/Lewis_Carroll",
          "https://en.wikipedia.org/wiki/William_Wordsworth",
          "https://en.wikipedia.org/wiki/Geoffrey_Chaucer",
          "https://en.wikipedia.org/wiki/Mary_Shelley",
          "https://en.wikipedia.org/wiki/Samuel_Taylor_Coleridge",
          "https://en.wikipedia.org/wiki/Aldous_Huxley",
          "https://en.wikipedia.org/wiki/Rudyard_Kipling",
          "https://en.wikipedia.org/wiki/Francis_Bacon",
          "https://en.wikipedia.org/wiki/Emily_Bront%C3%AB",
          "https://en.wikipedia.org/wiki/D._H._Lawrence",
          "https://en.wikipedia.org/wiki/Jonathan_Swift",
          "https://en.wikipedia.org/wiki/T._S._Eliot",
          "https://en.wikipedia.org/wiki/John_Milton",
          "https://en.wikipedia.org/wiki/Samuel_Johnson",
          "https://en.wikipedia.org/wiki/H._G._Wells",
          "https://en.wikipedia.org/wiki/Alfred,_Lord_Tennyson",
          "https://en.wikipedia.org/wiki/E._M._Forster",
          "https://en.wikipedia.org/wiki/Wilfred_Owen",
          "https://en.wikipedia.org/wiki/Evelyn_Waugh",
          "https://en.wikipedia.org/wiki/Agatha_Christie",
          "https://en.wikipedia.org/wiki/Homer",
          "https://en.wikipedia.org/wiki/Euripides",
          "https://en.wikipedia.org/wiki/Aristotle",
          "https://en.wikipedia.org/wiki/Plato",
          "https://en.wikipedia.org/wiki/Sophocles",
          "https://en.wikipedia.org/wiki/Aristophanes",
          "https://en.wikipedia.org/wiki/Herodotus",
          "https://en.wikipedia.org/wiki/Aeschylus",
          "https://en.wikipedia.org/wiki/Thucydides",
          "https://en.wikipedia.org/wiki/Nikos_Kazantzakis",
          "https://en.wikipedia.org/wiki/Sappho",
          "https://en.wikipedia.org/wiki/Plutarch",
          "https://en.wikipedia.org/wiki/Hesiod",
          "https://en.wikipedia.org/wiki/Xenophon",
          "https://en.wikipedia.org/wiki/Demosthenes",
          "https://en.wikipedia.org/wiki/Aesop"
          )


countries <- c(rep("Russia", 25), rep("United States",28), rep("France", 21), rep("United Kingdom", 33), rep("Greece", 16))

##Initialize tibble that bio_sentiments table will fill
biographies <- as.tibble(data.frame(author=character(0), country = character(0), Mean_Bio_Score=numeric(0), stringsAsFactors = FALSE))

##Function that produces a tibble of Sentiments of Author Biographies
bio_sentiments <- function(urls, countries){

  
  if(length(urls) != length(countries)){
    stop ("Both lists must be of equal length")
  }
  for(i in 1:length(urls)){
    
    #Convert webpage text from list of lists, to one large list of all text
    url<- urls[i]
    bio <- url %>% 
      read_html() %>% 
      html_nodes("p") %>% 
      html_text() %>% 
      unlist() 
    
    #Convert list of text into a tibble of words with sentiment score
    bio <- tibble(text = bio) %>% 
      mutate(paragraph = row_number()) %>% 
      unnest_tokens(word,text) %>% 
      anti_join(stop_words) %>% 
      inner_join(get_sentiments("afinn")) 
    
    author <- str_split(url,"/")[[1]][5]
    result <- mean(bio$score)
    country <- countries[i]
    
    ##Add row of data to tibble
    biographies <- add_row(biographies, author = author, country = country, Mean_Bio_Score = result)
  }
  
  ##Return filled out tibble as result
  biographies
}

##Create Biography Sentiments table
biographies <- bio_sentiments(urls,countries)

#Make authors.nrc table to store authors and the NRC emotions they use in writing
authors.nrc <- as.tibble(data.frame(author=character(0), 
                                    anger.prop=numeric(0), 
                                    anticipation.prop=numeric(0),
                                    disgust.prop=numeric(0),
                                    fear.prop=numeric(0),
                                    joy.prop=numeric(0),
                                    sadness.prop=numeric(0),
                                    surprise.prop=numeric(0),
                                    trust.prop=numeric(0),
                                    stringsAsFactors = FALSE))

#Function to insert nrc scores for each author in author.nrc table
nrc_sentiments <- function(author, book_ids){
  
  books <-gutenberg_download(gutenberg_id = book_ids) %>% 
    unnest_tokens(word,text) %>% 
    anti_join(stop_words) %>% 
    inner_join(get_sentiments("nrc"))
  
  emotions.tbl <- books %>% 
    group_by(sentiment) %>% 
    summarise(count = length(sentiment))
  
  
  sents <- c("anger", "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust") 
  
  #Get total number of emotionally charged words used by author
  total <- emotions.tbl %>% filter(sentiment %in% sents) %>% select(count) %>% sum
  
  #Find proportion of words by author affiliated with anger, fear, disgust etc.
  anger <- emotions.tbl %>% filter(sentiment == "anger") %>% select(count) %>% as.numeric()
  anger <- anger/total
  
  anticipation <- emotions.tbl %>% filter(sentiment == "anticipation") %>% select(count) %>% as.numeric()
  anticipation <- anticipation/total
  
  disgust <- emotions.tbl %>% filter(sentiment == "disgust") %>% select(count) %>% as.numeric()
  disgust <- disgust/total
  
  fear <- emotions.tbl %>% filter(sentiment == "fear") %>% select(count) %>% as.numeric()
  fear <- fear/total
  
  joy <- emotions.tbl %>% filter(sentiment == "joy") %>% select(count) %>% as.numeric()
  joy <- joy/total
  
  sadness <- emotions.tbl %>% filter(sentiment == "sadness") %>% select(count) %>% as.numeric()
  sadness<- sadness/total
  
  surprise <- emotions.tbl %>% filter(sentiment == "surprise") %>% select(count) %>% as.numeric()
  surprise <- surprise/total
  
  trust <- emotions.tbl %>% filter(sentiment == "trust") %>% select(count) %>% as.numeric()
  trust <- trust/total
  
  #Insert proportions into authors.nrc table
  
  authors.nrc <- add_row(authors.nrc, 
                         author = author, 
                         anger.prop = anger, 
                         anticipation.prop = anticipation,
                         disgust.prop = disgust,
                         fear.prop = fear,
                         joy.prop = joy,
                         sadness.prop = sadness,
                         surprise.prop = surprise,
                         trust.prop = trust)
  
}

#Russian Authors
authors.nrc <- nrc_sentiments("Leo_Tolstoy", book_ids = c(1399,2600))
authors.nrc <- nrc_sentiments("Fyodor_Dostoevsky", book_ids = c(2197,2554,2638,28054,8117))
authors.nrc <- nrc_sentiments("Nikolai_Gogol", book_ids = c(1081,36238))
authors.nrc <- nrc_sentiments("Ivan_Turgenev", book_ids = c(30723,8597,8744))
authors.nrc <- nrc_sentiments("Anton_Chekhov", book_ids = c(1753,1732,13414))
authors.nrc <- nrc_sentiments("Maxim_Gorky", book_ids = c(681,2288,2709,3783,51094))
authors.nrc <- nrc_sentiments("Alexander_Pushkin", book_ids = c(4344,5089,13511,23058))
authors.nrc <- nrc_sentiments("Ivan_Bunin", book_ids = c(44998))
authors.nrc <- nrc_sentiments("Mikhail_Lermontov", book_ids = c(913))
authors.nrc <- nrc_sentiments("F._Scott_Fitzgerald", book_ids = c(805,6695,9830))

#American Authors
authors.nrc <- nrc_sentiments("Mark_Twain", book_ids = c(74,76,86,1837))
authors.nrc <- nrc_sentiments("Nathaniel_Hawthorne", book_ids = c(33,77))
authors.nrc <- nrc_sentiments("Herman_Melville", book_ids = c(15))
authors.nrc <- nrc_sentiments("Edith_Wharton", book_ids = c(284,541))
authors.nrc <- nrc_sentiments("Kurt_Vonnegut", book_ids = c(21279,30240))
authors.nrc <- nrc_sentiments("Emily_Dickinson", book_ids = c(2678,2679,12242))
authors.nrc <- nrc_sentiments("Ray_Bradbury", book_ids = c(41622,41624,41627,51171))
authors.nrc <- nrc_sentiments("Sinclair_Lewis", book_ids = c(543,1156))
authors.nrc <- nrc_sentiments("Sherwood_Anderson", book_ids = c(416,7048))
authors.nrc <- nrc_sentiments("Henry_David_Thoreau", book_ids = c(205))

#French Authors
authors.nrc <- nrc_sentiments("Marcel_Proust", book_ids = c(7178))
authors.nrc <- nrc_sentiments("Gustave_Flaubert", book_ids = c(25053,25014,27537,27575,34828,4609))
authors.nrc <- nrc_sentiments("Victor_Hugo", book_ids = c(2610))
authors.nrc <- nrc_sentiments("%C3%89mile_Zola ", book_ids = c(1069,5135,5744,6626,7011,9499,10330,10720,13851,13695))
authors.nrc <- nrc_sentiments("Honor%C3%A9_de_Balzac", book_ids = c(1237,469,1189,1196,1215,1223,1230,
                                                                 1242,1277,1294,1305,1307,1343,1344,1345,
                                                                 1350,1352,1357,1369,1373,1374,1380,1389,1403,1405,
                                                                 1410,1411,1425,1426,1427,1428,1432,1433,1437,1443,
                                                                 1453,1454,1455,1456,1474,1475,1481,1482,1553,1554,
                                                                 1555,1556,1559,1569,1639,1641,1649,1659,1680,1683,1704,1710,
                                                                 1714,1715,1729,1737,1749,1810,1811,1813,1826,1841,1854,
                                                                 1856,1871,1873,1884,1899,1912,1921,1940,1941,1942,1943,
                                                                 1950,1954,1957,1967,5873,7416,7927,7929,7950,7958,8079,
                                                                 12900,13159))
authors.nrc <- nrc_sentiments("Voltaire", book_ids = c(18569,19942,18972))
authors.nrc <- nrc_sentiments("Alexandre_Dumas", book_ids = c(965,1257,1258,1259,2759,1189))
authors.nrc <- nrc_sentiments("Charles_Bauderlaire", book_ids = c(36098))
authors.nrc <- nrc_sentiments("Jules_Verne", book_ids = c(83,103,164,3748))
authors.nrc <- nrc_sentiments("Guy_de_Maupassant", book_ids = c(7114,7549,3090))
authors.nrc <- nrc_sentiments("Denis_Diderot", book_ids = c(34544))
authors.nrc <- nrc_sentiments("Ren%C3%A9_Descartes", book_ids = c(59,4391))
authors.nrc <- nrc_sentiments("Stendhal", book_ids = c(44747))

#British Authors
authors.nrc <- nrc_sentiments("Charles_Dickens", book_ids = c(46,98,564,580,700,730,766,883,963,967,968,1023,1400))
authors.nrc <- nrc_sentiments("Jane_Austen", book_ids = c(105,121,141,158,161,1342,946))
authors.nrc <- nrc_sentiments("Charlotte_Bront%C3%AB", book_ids = c(1028,1260,9182,30486))
authors.nrc <- nrc_sentiments("George_Eliot", book_ids = c(145,507,550,6688))
authors.nrc <- nrc_sentiments("Thomas_Hardy", book_ids = c(110,153))
authors.nrc <- nrc_sentiments("William_Shakespeare", book_ids = c(1041,1045,seq(1500,1544),2247,2250,seq(2253,2260),2262,2265,2266,2267))
authors.nrc <- nrc_sentiments("Virginia_Woolf", book_ids = c(144,1245,5670,29220))
authors.nrc <- nrc_sentiments("Joseph_Conrad", book_ids = c(219,220,1083,974,2021,5658))
authors.nrc <- nrc_sentiments("Lewis_Carroll", book_ids = c(11,12,13))
authors.nrc <- nrc_sentiments("William_Wordsworth", book_ids = c(8774,8824,8905,8912,10219,12145,12383,32459))
authors.nrc <- nrc_sentiments("Geoffrey_Chaucer", book_ids = c(257,2383))
authors.nrc <- nrc_sentiments("Mary_Shelley", book_ids = c(61))
authors.nrc <- nrc_sentiments("Rudyard_Kipling", book_ids = c(236,21777,1937))
authors.nrc <- nrc_sentiments("Franics_Bacon", book_ids = c(575,2434,5500))
authors.nrc <- nrc_sentiments("Emily_Bront%C3%AB", book_ids = c(768))

#Greek Authors
authors.nrc <- nrc_sentiments("HomerB", book_ids = c(2199,3160))
authors.nrc <- nrc_sentiments("Euripides", book_ids = c(15081,35170,35171,35173,35451,10523))
authors.nrc <- nrc_sentiments("Aristotle", book_ids = c(1974,2412,6762,6763))
authors.nrc <- nrc_sentiments("Plato", book_ids = c(150))
authors.nrc <- nrc_sentiments("Sophocles", book_ids = c(31))
authors.nrc <- nrc_sentiments("Aristophanes", book_ids = c(2562,2571,3012,3013,7700,7998))
authors.nrc <- nrc_sentiments("Thucydides", book_ids = c(9074))
authors.nrc <- nrc_sentiments("Sappho", book_ids = c(42166))
authors.nrc <- nrc_sentiments("Hesiod", book_ids = c(348))
authors.nrc <- nrc_sentiments("Demosthenes", book_ids = c(9060,9061))
authors.nrc <- nrc_sentiments("Aesop", book_ids = c(21))

authors <- as.tibble(data.frame(author=character(0), Mean_Book_Score=numeric(0), stringsAsFactors = FALSE))

##Sentiments by Authors function

book_sentiments <- function(author, book_ids){
  
  books <-gutenberg_download(gutenberg_id = book_ids) %>% 
    unnest_tokens(word,text) %>% 
    anti_join(stop_words) %>% 
    inner_join(get_sentiments("afinn"))
    
  result <- mean(books$score)
  authors <- add_row(authors, author = author, Mean_Book_Score = result)
}

#Russian Authors
authors <- book_sentiments("Leo_Tolstoy", book_ids = c(1399,2600))
authors <- book_sentiments("Fyodor_Dostoevsky", book_ids = c(2197,2554,2638,28054,8117))
authors <- book_sentiments("Nikolai_Gogol", book_ids = c(1081,36238))
authors <- book_sentiments("Ivan_Turgenev", book_ids = c(30723,8597,8744))
authors <- book_sentiments("Anton_Chekhov", book_ids = c(1753,1732,13414))
authors <- book_sentiments("Maxim_Gorky", book_ids = c(681,2288,2709,3783,51094))
authors <- book_sentiments("Alexander_Pushkin", book_ids = c(4344,5089,13511,23058))
authors <- book_sentiments("Ivan_Bunin", book_ids = c(44998))
authors <- book_sentiments("Mikhail_Lermontov", book_ids = c(913))
authors <- book_sentiments("F._Scott_Fitzgerald", book_ids = c(805,6695,9830))

#American Authors
authors <- book_sentiments("Mark_Twain", book_ids = c(74,76,86,1837))
authors <- book_sentiments("Nathaniel_Hawthorne", book_ids = c(33,77))
authors <- book_sentiments("Herman_Melville", book_ids = c(15))
authors <- book_sentiments("Edith_Wharton", book_ids = c(284,541))
authors <- book_sentiments("Kurt_Vonnegut", book_ids = c(21279,30240))
authors <- book_sentiments("Emily_Dickinson", book_ids = c(2678,2679,12242))
authors <- book_sentiments("Ray_Bradbury", book_ids = c(41622,41624,41627,51171))
authors <- book_sentiments("Sinclair_Lewis", book_ids = c(543,1156))
authors <- book_sentiments("Sherwood_Anderson", book_ids = c(416,7048))
authors <- book_sentiments("Henry_David_Thoreau", book_ids = c(205))

#French Authors
authors <- book_sentiments("Marcel_Proust", book_ids = c(7178))
authors <- book_sentiments("Gustave_Flaubert", book_ids = c(25053,25014,27537,27575,34828,4609))
authors <- book_sentiments("Victor_Hugo", book_ids = c(2610))
authors <- book_sentiments("%C3%89mile_Zola ", book_ids = c(1069,5135,5744,6626,7011,9499,10330,10720,13851,13695))
authors <- book_sentiments("Honor%C3%A9_de_Balzac", book_ids = c(1237,469,1189,1196,1215,1223,1230,
                                                                 1242,1277,1294,1305,1307,1343,1344,1345,
                                                                 1350,1352,1357,1369,1373,1374,1380,1389,1403,1405,
                                                                 1410,1411,1425,1426,1427,1428,1432,1433,1437,1443,
                                                                 1453,1454,1455,1456,1474,1475,1481,1482,1553,1554,
                                                                 1555,1556,1559,1569,1639,1641,1649,1659,1680,1683,1704,1710,
                                                                 1714,1715,1729,1737,1749,1810,1811,1813,1826,1841,1854,
                                                                 1856,1871,1873,1884,1899,1912,1921,1940,1941,1942,1943,
                                                                 1950,1954,1957,1967,5873,7416,7927,7929,7950,7958,8079,
                                                                 12900,13159))
authors <- book_sentiments("Voltaire", book_ids = c(18569,19942,18972))
authors <- book_sentiments("Alexandre_Dumas", book_ids = c(965,1257,1258,1259,2759,1189))
authors <- book_sentiments("Charles_Bauderlaire", book_ids = c(36098))
authors <- book_sentiments("Jules_Verne", book_ids = c(83,103,164,3748))
authors <- book_sentiments("Guy_de_Maupassant", book_ids = c(7114,7549,3090))
authors <- book_sentiments("Denis_Diderot", book_ids = c(34544))
authors <- book_sentiments("Ren%C3%A9_Descartes", book_ids = c(59,4391))
authors <- book_sentiments("Stendhal", book_ids = c(44747))

#British Authors
authors <- book_sentiments("Charles_Dickens", book_ids = c(46,98,564,580,700,730,766,883,963,967,968,1023,1400))
authors <- book_sentiments("Jane_Austen", book_ids = c(105,121,141,158,161,1342,946))
authors <- book_sentiments("Charlotte_Bront%C3%AB", book_ids = c(1028,1260,9182,30486))
authors <- book_sentiments("George_Eliot", book_ids = c(145,507,550,6688))
authors <- book_sentiments("Thomas_Hardy", book_ids = c(110,153))
authors <- book_sentiments("William_Shakespeare", book_ids = c(1041,1045,seq(1500,1544),2247,2250,seq(2253,2260),2262,2265,2266,2267))
authors <- book_sentiments("Virginia_Woolf", book_ids = c(144,1245,5670,29220))
authors <- book_sentiments("Joseph_Conrad", book_ids = c(219,220,1083,974,2021,5658))
authors <- book_sentiments("Lewis_Carroll", book_ids = c(11,12,13))
authors <- book_sentiments("William_Wordsworth", book_ids = c(8774,8824,8905,8912,10219,12145,12383,32459))
authors <- book_sentiments("Geoffrey_Chaucer", book_ids = c(257,2383))
authors <- book_sentiments("Mary_Shelley", book_ids = c(61))
authors <- book_sentiments("Rudyard_Kipling", book_ids = c(236,21777,1937))
authors <- book_sentiments("Franics_Bacon", book_ids = c(575,2434,5500))
authors <- book_sentiments("Emily_Bront%C3%AB", book_ids = c(768))

#Greek Authors
authors <- book_sentiments("HomerB", book_ids = c(2199,3160))
authors <- book_sentiments("Euripides", book_ids = c(15081,35170,35171,35173,35451,10523))
authors <- book_sentiments("Aristotle", book_ids = c(1974,2412,6762,6763))
authors <- book_sentiments("Plato", book_ids = c(150))
authors <- book_sentiments("Sophocles", book_ids = c(31))
authors <- book_sentiments("Aristophanes", book_ids = c(2562,2571,3012,3013,7700,7998))
authors <- book_sentiments("Thucydides", book_ids = c(9074))
authors <- book_sentiments("Sappho", book_ids = c(42166))
authors <- book_sentiments("Hesiod", book_ids = c(348))
authors <- book_sentiments("Demosthenes", book_ids = c(9060,9061))
authors <- book_sentiments("Aesop", book_ids = c(21))

```

## Introduction

The idea behind this project was to see if the happiness ranking of a country as given by the 2017 Gallup poll was reflected in the happiness of the major literary works from that country. I used three data sources to do this; Wikipedia, R-Gutenberg package, and the Gallup 2017 Happiness poll data. 

First I decided to look at overall happiness trends throughout the world. Then I zeroed in on 5 countries in particular; Russia, Greece, France, USA and the UK and explored the happiness trends in those countries. The reason I chose these countries, is the R-Gutenberg package mainly contains Western authors. I would have been very interested to do a East vs West analysis of literary and happiness trends, but unfortunately the Gutenberg package doesn't contain many Eastern authors.

##The Happiest Places 

```{r The Happiest Places, echo = FALSE, message = FALSE}
library(reshape2)
setwd("C:/Users/George/Documents/Rutgers/Data Wrangling/Project")
happy17 <- read_csv("C:/Users/George/Documents/Rutgers/Data Wrangling/Project/2017_happiness.csv")
happy16 <- read_csv("C:/Users/George/Documents/Rutgers/Data Wrangling/Project/2016_happiness.csv")

#Join happy16 and happy17 to get Regions from 2016 data which is missing in 2017 data. And clean column names
happy <- happy17 %>% 
  left_join(select(happy16, Country, Region))

happy <- happy %>% 
  rename(GDP = Economy..GDP.per.Capita.,
         Health = Health..Life.Expectancy.,
         `Government Corruption` = Trust..Government.Corruption.
         )
happy %>% 
  head(n=10) %>% 
  select(Happiness.Rank, Country, Region, Happiness.Score)
```

## The Unhappiest Places

```{r Unhappy Places, echo = FALSE, message = FALSE}
happy %>% 
  tail(n=10) %>% 
  select(Happiness.Rank, Country, Region, Happiness.Score)

```

Above we see that most of the high-ranking countries are either in Europe or Australia while the low-ranking countries are in Africa. The top countries and lowest ranked countries also differ in what variables they consider important to their happiness.

##Happiness Variable Contribution by Ranking

Here we see that the top 10 countries seem to have a consensus on what makes them happy. GDP and Family are both most important followed by Health, Freedom, Generosity and Government Corruption.  

The bottom 10 countries have much less consensus on what makes them happy. They all do seem to value Family however.
```{r Happiness Variable Contribution for Top 10 Countries, echo = FALSE, message = FALSE}
top10 <- c("Norway", "Denmark", "Iceland", "Switzerland", "Finland", "Netherlands", "Canada", "New Zealand", "Sweden", "Australia")

#Melt variables by country so we can plot
happy_by_country <- happy %>% 
  select(Country, GDP:`Government Corruption`) %>% 
  melt(id = c("Country"))

happy_by_country %>% 
  filter(Country %in% top10) %>% 
  ggplot(mapping = aes(variable, value)) +
  geom_line(aes(color = Country, group = Country)) +
  xlab("Happiness Variables") + ylab("Score Contribution") + ggtitle("Happiness Variable Score Contribution for Top 10 Countries") +
  scale_x_discrete(labels = function(variable) str_wrap(variable, width = 5))
```

```{r Happiness Variable Contribution for Bottom 10 Countries, echo = FALSE, message = FALSE}
low10 <- c("Yemen", "South Sudan", "Liberia", "Guinea", "Togo", "Rwanda", "Syria", "Tanzania", "Burundi", "Central African Republic")

#Plot low 10 countries
happy_by_country %>% 
  filter(Country %in% low10) %>% 
  ggplot(mapping = aes(variable, value)) +
  geom_line(aes(color = Country, group = Country)) +
  xlab("Happiness Variables") + ylab("Score Contribution") + ggtitle("Happiness Variable Score Contribution for Low 10 Countries") +
  scale_x_discrete(labels = function(variable) str_wrap(variable, width = 5))
```

##Happiness by Region

The average happiness by world region is not too surprising. Overall, more developed regions seem to report happier citizens.
```{r Happiness by Region, echo = FALSE, message = FALSE, warning = FALSE}
happy %>% 
  filter(is.na(Region) != TRUE) %>% 
  ggplot(mapping = aes(x = reorder(Region, Happiness.Score, mean), Happiness.Score)) +
  geom_boxplot(aes(fill = Region)) +
  xlab("World Region") +ggtitle("Happiness Score by Region") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black")) +
  scale_x_discrete(labels = function(Region) str_wrap(Region, width = 5))
```

## Happiness Variables by World Region

There do appear to be some differences in what each world region considers most important to their happiness. In North America and Western Europe, GDP seems to be most important in determining happiness. However, in all the other regions, Family ranks higher than GDP. This is most visible in Sub-Saharan AFrica, Asia and the Latin American regions.
```{r Happiness Variables by World Region, echo = FALSE, message = FALSE}
#Melt happiness variables into region so we can plot
happy_by_region <- happy %>% 
  select(Region, GDP:`Government Corruption`) %>% 
  melt(id = c("Region"))

#Happiness Variable contribution by Region
happy_by_region %>% 
  filter(is.na(Region) != TRUE) %>% 
  ggplot(mapping = aes(variable, value)) +
  geom_boxplot(aes(fill = Region)) +
  scale_x_discrete(labels = function(variable) str_wrap(variable, width = 10)) +
  xlab("Happiness Variables") + ylab("Score Contribution") + ggtitle("Happiness Variable Contribution Levels by World Region") +
  theme_grey(base_size = 4) +
  theme(legend.position = "none") + 
  facet_wrap(~ Region)

```

##5 Countries Overview

The next part of the report focuses on the happiness and literary analysis of our 5 selected countries. First, we examine their happiness rankings to get a general picture of their overall happiness.

```{r 5 countries, echo = FALSE, message = FALSE}
country.list <- c("Russia", "United States", "Greece", "France", "United Kingdom")

print(happy %>% 
  filter(Country %in% country.list) %>% 
  select(Happiness.Rank, Country, Happiness.Score, GDP, Family, Health, Freedom, Generosity, `Government Corruption`), width = Inf)

happy_by_country %>% 
  filter(Country %in% country.list) %>% 
  ggplot(mapping = aes(variable, value)) +
  geom_line(aes(color = Country, group = Country)) +
  xlab("Happiness Variable") + ylab("Score Contribution") + ggtitle("Happiness Variable Contributions") +
  theme_grey(base_size = 10) +
  scale_x_discrete(labels = function(variable) str_wrap(variable, width = 5))
```

##Method 

For each of the five countries examined I scraped the Wikipedia pages of 20-30 of its most prominent authors. I then scored the pages using the AFINN lexicon for its positive vs negative sentiment. I reasoned authors with more negative biographies, probably led unhappier lives. Conversely, those with more positive biographies led happier lives. I assigned each author a "Mean Bio Score"

I then used the R-Gutenberg package to score the major literary works of these authors using both the AFINN and NRC lexicons and assigned each author a “Mean Book Score” for the overall positivity/negativity of their body of work.  

Finally, I joined the "Mean Bio Scores", "Mean Book Scores" and "NRC Scores" on author into one large table. The table required some light regex cleaning to deal with the accents in some of the authors' name.

The NRC lexicon was used to find the proportion of words used by each author corresponding to emotions like “joy” and “fear”.  

The AFINN lexicon was used since it applies a score to words ranging from -5 to 5. I found this lexicon more nuanced than the BING lexicon which simply categorizes words into 1 or -1 scores. For example, with BING, the phrase “tortured and exiled” would receive the same negative score as “unhappy and sad childhood” which I didn’t think was adequate.  

Below is a snapshot of the final table produced.

```{r Authors snapshot, echo = FALSE, message = FALSE}
authors_and_bios <- biographies %>% 
  left_join(authors) %>% 
  left_join(authors.nrc)

#Clean up e with accents in Authors column of authors_and_bios
authors_and_bios$author <- str_replace_all(authors_and_bios$author, "%.*%[A-Z|1-9][A-Z|1-9]", "e")
#Clean up O in Flannery O Connor
authors_and_bios$author <- str_replace_all(authors_and_bios$author, "O%[1-9]{2}", "O'")
#Get rid of underscores in names
authors_and_bios$author <- str_replace_all(authors_and_bios$author, "_", " ")

print(authors_and_bios)
```

##Literary Analysis

Now we can look at some plots and see if there are any relationships between the happiness of an author, and the overall sentiment of their work. We will also examine whether an author's native country's happiness is related to their own happiness, as well as the overall sentiment of their work.

Here I plotted the author's happiness against the sentiment scores of their books. I was hoping to see a linear relationship, that happier authors write happier books. But for the most part, this does not seem to be the case, with a large cluster of the authors hovering around the 0 score on both book sentiment and biography sentiment.

```{r Book Sentiments vs Author Happiness, echo = FALSE, message = FALSE}
authors_and_bios %>%
  filter(is.na(Mean_Book_Score) == FALSE) %>% 
  ggplot(mapping = aes(Mean_Bio_Score, Mean_Book_Score)) +
  geom_point(aes(color = country), size=2) +
  geom_vline(xintercept = 0) +
  geom_hline(yintercept = 0) +
  geom_text(aes(label=author), size = 2, nudge_y = .025) +
  theme_grey(base_size = 10) +
  xlab("Mean Biography Score") + ylab("Mean Book Score")
```

```{r Authors Happiness by Country, echo = FALSE, message = FALSE, warning = FALSE}
authors_and_bios %>% 
  mutate(country = reorder(country, Mean_Bio_Score)) %>% 
  ggplot(mapping = aes(country,Mean_Bio_Score)) +
  geom_boxplot(aes(fill = country)) +
  xlab("Country") + ylab("Mean Biography Score") + ggtitle("Author's Happiness by Country") +
  theme_grey(base_size = 10) +
  theme(legend.position = "none") 
```

```{r Average Book Sentiment by Country, echo = FALSE, message = FALSE, warning = FALSE}
authors_and_bios %>% 
  mutate(country = reorder(country, Mean_Book_Score)) %>%
  ggplot(mapping = aes(country,Mean_Book_Score)) +
  geom_boxplot(aes(fill = country)) +
  xlab("Country") + ylab("Mean Book Score") + ggtitle("Average Book Sentiment by Country") +
  theme_grey(base_size = 10) +
  theme(legend.position = "none") 
```

##NRC Analysis

Now I examine how each country and the authors from those countries differed in their use of NRC words like "joy", "surprise", "anger" etc. I had hoped for a pattern to emerge, like American authors used more "pride" word on average than other countries. However, what emerged was the fact that the proportion of NRC emotion words used by each country was about the same.

To perform these analyses, I had to gather the NRC variables in my authors_and_bios table in order to be able to plot them all together.

```{r NRC Analysis, echo = FALSE, message = FALSE, warning = FALSE}
#Create a new tibble with NRC emotions by country stacked on each other so boxplots can be made
emotions_by_country <- authors_and_bios %>% 
  select(country, anger.prop:trust.prop) %>% 
  melt(id = "country")

#Emotion names list to use in emotions_labeller function
emotion_names <- list(
  "anger.prop" = "Anger",
  "anticipation.prop" = "Anticipation",
  "disgust.prop" = "Disgust",
  "fear.prop" = "Fear",
  "joy.prop" = "Joy",
  "sadness.prop" = "Sadness",
  "surprise.prop" = "Surprise",
  "trust.prop" = "Trust"
)

#Emotions labeller function to use in re-writing facet wrap labels so the titles look better than anger.prop
emotions_labeller <- function(variable,value){
  return (emotion_names[value])
}

#Boxplots of NRC emotions by country
emotions_by_country %>% 
  ggplot(mapping = aes(country, value)) +
  geom_boxplot(aes(fill = country)) +
  facet_wrap(~variable, labeller = emotions_labeller) +
  xlab("Country") + ylab("Proportion") + ggtitle("Proportion of NRC Words used by Country") +
  theme_grey(base_size = 8) +
  scale_x_discrete(labels = function(country) str_wrap(country, width = 5))

#Create a new tibble with NRC emotions by author stacked on each other so dotplots can be made
emotions_by_author <- authors_and_bios %>% 
  select(author, country, anger.prop:trust.prop) %>% 
  melt(id = c("author", "country"))

#Emotions by Russian Authors
emotions_by_author %>% 
  filter(country == "Russia") %>% 
  ggplot(mapping = aes(author, value)) +
  geom_point(aes(fill = country)) +
  geom_label_repel(aes(label = author), segment.color = NA, size = 1.5) +
  facet_wrap(~variable, labeller = emotions_labeller) +
  theme_grey(base_size = 10) +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  xlab("Author") + ylab("Proportion") + ggtitle("NRC Words used by Russian Authors")

#Emotions by British Authors
emotions_by_author %>% 
  filter(country == "United Kingdom") %>% 
  ggplot(mapping = aes(author, value)) +
  geom_point(aes(fill = country)) +
  geom_label_repel(aes(label = author), segment.color = NA, size = 1.5) +
  facet_wrap(~variable, labeller = emotions_labeller) +
  theme_grey(base_size = 10) +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  xlab("Author") + ylab("Proportion") + ggtitle("NRC Words used by UK Authors") 

#Emotions by French Authors
emotions_by_author %>% 
  filter(country == "France") %>% 
  ggplot(mapping = aes(author, value)) +
  geom_point(aes(fill = country)) +
  geom_label_repel(aes(label = author), segment.color = NA, size = 1.5) +
  facet_wrap(~variable, labeller = emotions_labeller) +
  theme_grey(base_size = 10) +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  xlab("Author") + ylab("Proportion") + ggtitle("NRC Words used by French Authors") 

#Emotions by Greek Authors
emotions_by_author %>% 
  filter(country == "Greece") %>% 
  ggplot(mapping = aes(author, value)) +
  geom_point(aes(fill = country)) +
  geom_label_repel(aes(label = author), segment.color = NA, size = 1.5) +
  facet_wrap(~variable, labeller = emotions_labeller) +
  theme_grey(base_size = 10) +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  xlab("Author") + ylab("Proportion") + ggtitle("NRC Words used by Greek Authors")

#Emotions by American Authors
emotions_by_author %>% 
  filter(country == "United States") %>% 
  ggplot(mapping = aes(author, value)) +
  geom_point(aes(fill = country)) +
  geom_label_repel(aes(label = author), segment.color = NA, size = 1.5) +
  facet_wrap(~variable, labeller = emotions_labeller) +
  theme_grey(base_size = 10) +
  theme(axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") +
  xlab("Author") + ylab("Proportion") + ggtitle("NRC Words used by American Authors")
```